manuscript_notes

### 2024-11-06 notes/manuscript_notes.Rmd
update notes

-> I clearly explained it..... todo

@@

-> I expected problems with fitting the very complex model M4. But even M3 has problems.

@@

-> added in

@@

-> I prefer the last option. I created a new figure 3.

@@

-> I think it is important for naive readers to get an idea of how the variables in the models presented later are calculated.

@@

-> Done todo

@@

-> done todo

@@

@@

-> Done... todo

@@

-> todo.  Done....

@@

>>>>

-> changed to: Note that duplicate terms across the interaction terms in the model formula (e.g., condition) are ignored.

@@

-> I expected problems with fitting the very complex model M4. I added this info.

@@

@@

-> I prefer the last option. I created a new figure 3 and added info to its caption.

@@

-> I think it is important for naive readers to get an idea of how the variables in the model formulas presented later are calculated.

@@

->  todo

@@

->  todo

@@

-> todo

@@

-> todo

@@

-> todo.

@@

# comments Sven 6 nov

1. Figure 1: connect the points per subject?

2.
